\begin{thebibliography}{99}
	\addcontentsline{toc}{chapter}{Список литературы} %добавляем в соодержание
	
	\bibitem {1} Levine R. Finance and growth: theory and evidence //Handbook of economic growth. – 2005. – Т. 1. – С. 865-934.
	\bibitem {2}	Fidrmuc J., Fungáčová Z., Weill L. Does bank liquidity creation contribute to economic growth? Evidence from Russia //Open Economies Review. – 2015. – Т. 26. – №. 3. – С. 479-496.
    \bibitem{3}	Cecchetti S. G., Kharroubi E. Why does financial sector growth crowd out real economic growth?. – 2015.
	\bibitem{4}	Berger A. N., Bouwman C. H. S. Bank liquidity creation //Review of Financial Studies. – 2009. – Т. 22. – №. 9. – С. 3779-3837.
	\bibitem{5}	King R. G., Levine R. Finance and growth: Schumpeter might be right //The quarterly journal of economics. – 1993. – Т. 108. – №. 3. – С. 717-737.
	\bibitem{6}	Stolbov M. Causality between credit depth and economic growth: Evidence from 24 OECD countries //Empirical Economics. – 2015. – С. 1-32.
	\bibitem{7}	Столбов М. И. Финансовый рынок и экономический рост: контуры проблемы //Научная книга. – 2008. – С. 58-61.
	\bibitem{8}	Ahmad E., Malik A. Financial sector development and economic growth: An empirical analysis of developing countries //Journal of Economic Cooperation and Development. – 2009. – Т. 30. – №. 1. – С. 17-40.
	\bibitem{9}	Stock J. H., Watson M. W. Introduction to econometrics. – Boston : Addison Wesley, 2003. – Т. 104.
	\bibitem{10}	Шагас Н. Л., Туманова Е. А. Макроэкономика-2 //Москва. – 2006.
	
\end{thebibliography}